Megan's code for Isoviz

### 2023-04-20 temp_code/MS_isoviz_code.Rmd
update Megan's code

```{r}
# libraries
require(readr)
require(dplyr)
require(tidyr)
require(magrittr)
require(ggplot2)
require(data.table)
require(stringr)
require(ggpubr)
require(grid)
require(gridExtra)
require(cowplot)

@@

@@

@@

output is a text file
-p MINCLURATIO, --mincluratio=MINCLURATIO
                        minimum fraction of reads in a cluster that support a
                        junction (default 0.001)

--includeconst
```{r}
# This is data from our A375 screen cells and is the most accurate for our work
# now this includes constitutive exons which have a single junction per cluster
# required 30 total reads per cluster and junction to be 10% of total
clusters <- read_tsv("~/isoviz/data-raw/a375_screen_cells_perind.constcounts.gz", col_names = FALSE, skip = 1) # 59,783
clusters %<>% 
  separate(X1, into = c("coords", "counts"), sep = " ") %>% 
  separate(counts, into = c("junc.counts", "cluster.counts"), sep = "/", convert = TRUE) %>%
  separate(coords, into = c("chr", "start", "end", "name"), sep = ":", convert = TRUE) %>% 
  separate(name, into = c("same", "cluster.n", "extra"), sep = "_") %>% 
  select(-same, -extra)

@@

# remove clusters with no counts
# filter out chrM and chrY clusters
clusters %<>% filter(cluster.counts > 0, chr != "chrY", chr != "chrM")
clusters_table = as.data.table(clusters)
save(clusters_table, file = "~/isoviz/data/HEK293_lfc_clusters.rda")

@@

# remove clusters with no counts
# filter out chrM and chrY clusters
clusters %<>% filter(cluster.counts > 0, chr != "chrY", chr != "chrM")
clusters_table = as.data.table(clusters)
save(clusters_table, file = "~/isoviz/data/hESC_lfc_clusters.rda")

@@

Write function to generate intron coords from exon coords- this is currently slow (~30 minutes), can we make the loop more efficient?
```{r}
# make psl with intron coords instead of exon
# adapted from genomedata.R

@@

to_plot = map_junction("ENSG00000001167.15") # NFYA
to_plot = map_junction("ENSG00000100320") # RBFOX2, alt start is missing because it's intron doesnt overlap another and counts are only 8 so included in consitutive either

@@

```{r}
load(file='~/isoviz/data/iso_data_complete.rda')
df = to_plot

@@

  # I am copying the plot_isoforms function here, figure out how to integrate these later
  gene = unique(df$gene_id)
  gene_trans =which(str_detect(iso_data_complete$gene_id, gene))
  gene_data = iso_data_complete[gene_trans,]

@@

plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/rbfox2_isoforms.pdf", width = 8, height = 8.5)
```

@@

to_plot = map_junction("ENSG00000001167.15", cell_type = "hESC") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/nfya_isoforms_hESC.pdf", width = 8, height = 2)

@@

to_plot = map_junction("ENSG00000100320", cell_type = "hESC") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/rbfox2_isoforms_hESC.pdf", width = 8, height = 8.5)

@@

Generate a junction file of all possible junctions sequences for Andrew to make predictions
- use gencode psl
- want to make sure to have junc id that will correspond to leafcutter (can merge by sequence at first)
- can make this information into a table
```{r}
load(file = "~/isoviz/data/iso_intron_data.rda")
iso_intron_data %>% group_by(transcript_type) %>% tally()
iso_intron_data %>% group_by(chr) %>% tally()
iso_intron_data %>% filter(is.na(chr))

# filter for protein coding and lncRNAs
iso_intron_pc = iso_intron_data %>% filter(transcript_type == "protein_coding" | transcript_type == "lncRNA")

# remove transcript ids and collapse on junction coords
collapsed_junctions = iso_intron_pc %>% select(-trans_id, -transcript_name, -gene_type, -transcript_type) %>% 
  distinct() %>% select(chr, start = intron_starts, end = intron_ends, gene_id, gene_name, strand) # 281,880 junctions- how many show any uniqueness?

# to address how many annotated isoforms have a truly unique junction
# first filter the genes with more than one transcript
iso_intron_pc %>% select(gene_id, trans_id) %>% distinct() # 85,586 transcripts
n_df = iso_intron_pc %>% select(gene_id, trans_id) %>% distinct() %>% group_by(gene_id) %>% mutate(n_transcripts = n()) %>% ungroup() # 33,413
gene_list = n_df %>% select(-trans_id) %>% distinct() %>% filter(n_transcripts > 1) %>% select(gene_id) # 17,035 genes have more than 1 isoform

iso_pc_df = iso_intron_pc %>% full_join(n_df) %>% filter(gene_id %in% gene_list$gene_id) %>%
  group_by(chr, intron_starts, intron_ends, gene_id, strand, gene_name, n_transcripts) %>% mutate(n_trans_per_junc = n(), commonality = round((n_trans_per_junc/n_transcripts)*100, 0)) %>%
  mutate(junction_category = ifelse(n_trans_per_junc == 1, "fully_unique", ifelse(commonality == 100, "common", "partial_unique"))) %>% ungroup()

# junction level numbers- there are ~50,000 fully unique junctions for pc genes, meaning they belong to a singular isoform
iso_pc_df %>% select(chr, intron_starts, intron_ends, strand, gene_id, gene_name, gene_type, junction_category) %>% distinct() %>% 
  group_by(gene_type, junction_category) %>% tally()

# isoform-level, how many isoforms are uniquely targetable
iso_pc_df %>% filter(junction_category == "fully_unique") %>% select(gene_id, gene_name, trans_id, transcript_name, gene_type) %>% distinct() # 47,657 transcripts are uniquely targetable
iso_pc_df %>% filter(junction_category == "fully_unique") %>% select(gene_id, gene_name, trans_id, transcript_name, gene_type) %>% distinct() %>%
  distinct(gene_name) # 16,801 genes

>>>>

```{r}
# libraries
require(readr)
require(dplyr)
require(tidyr)
require(magrittr)
require(ggplot2)
require(data.table)
require(stringr)
require(ggpubr)
require(grid)
require(gridExtra)
require(cowplot)
require(Biostrings)
require(rempsyc) # for fancy tables: https://cran.r-project.org/web/packages/rempsyc/vignettes/table.html

@@

module load python/2.7.8

/gpfs/commons/home/mschertzer/knowles_lab/Megan/230320_cas13_validation/junctions

@@

# moderate stringency
python ~/Downloads/leafcutter/clustering/leafcutter_cluster_regtools.py -j 21c_hESC_RB2_empty_for_lfc.txt -m 20 -p 0.01 -o 21c_hESC_RB2_empty_p.01 -l 500000 --includeconst --checkchrom

@@

python ~/Downloads/leafcutter/clustering/leafcutter_cluster_regtools.py -j 21c_hESC_RB2_empty_for_lfc.txt -m 1 -p 0.01 -o hesc_all_junctions_lfc -l 500000 --includeconst --checkchrom

output is a text file
-p MINCLURATIO, --mincluratio=MINCLURATIO
                        minimum fraction of reads in a cluster that support a
                        junction (default 0.001)
-m MINCLUREADS, --minclureads=MINCLUREADS
                        minimum reads in a cluster (default 30 reads)                       
--includeconst
            also include constitutive introns

Inputs leafcutter clustering output and outputs formatted table
```{r}
# This is data from our A375 screen cells and is the most accurate for our work
# now this includes constitutive exons which have a single junction per cluster
# required 30 total reads per cluster and junction to be 10% of total
clusters <- read_tsv("~/isoviz/data-raw/a375_screen_cells_perind.constcounts.gz", col_names = FALSE, skip = 1) # 59,783
clusters %<>% 
  separate(X1, into = c("coords", "counts"), sep = " ") %>% 
  separate(counts, into = c("junc.counts", "cluster.counts"), sep = "/", convert = TRUE) %>%
  separate(coords, into = c("chr", "start", "end", "name"), sep = ":", convert = TRUE) %>% 
  separate(name, into = c("same", "cluster.n", "extra"), sep = "_") %>% 
  select(-same, -extra)

@@

clusters %<>% filter(cluster.counts > 0, chr != "chrY", chr != "chrM")
clusters_table = as.data.table(clusters)
save(clusters_table, file = "~/isoviz/data/HEK293_lfc_clusters.rda")

@@

clusters %<>% filter(cluster.counts > 0, chr != "chrY", chr != "chrM")
clusters_table = as.data.table(clusters)
save(clusters_table, file = "~/isoviz/data/hESC_lfc_clusters.rda")

# hESC- medium stringent
clusters <- read_tsv("~/isoviz/data-raw/21c_hESC_RB2_empty_p.01_perind.constcounts.gz", col_names = FALSE, skip = 1)
clusters %<>% 
  separate(X1, into = c("coords", "counts"), sep = " ") %>% 
  separate(counts, into = c("junc.counts", "cluster.counts"), sep = "/", convert = TRUE) %>%
  separate(coords, into = c("chr", "start", "end", "name"), sep = ":", convert = TRUE) %>% 
  separate(name, into = c("same", "cluster.n", "extra"), sep = "_") %>% 
  select(-same, -extra)

clusters %<>% filter(cluster.counts > 0, chr != "chrY", chr != "chrM")
clusters_table = as.data.table(clusters)
save(clusters_table, file = "~/isoviz/data/hESC_med_string_lfc_clusters.rda")

# Consider all junction counts and use gencode annotations to define unique versus common
```{r}
clusters <- read_tsv("~/isoviz/data-raw/hesc_all_junctions_lfc_perind.constcounts.gz", col_names = FALSE, skip = 1)
clusters %<>% 
  separate(X1, into = c("coords", "counts"), sep = " ") %>% 
  separate(counts, into = c("junc.counts", "cluster.counts"), sep = "/", convert = TRUE) %>%
  separate(coords, into = c("chr", "start", "end", "name"), sep = ":", convert = TRUE) %>% 
  separate(name, into = c("same", "cluster.n", "extra"), sep = "_") %>% 
  select(-same, -extra)

clusters %<>% filter(cluster.counts > 0, chr != "chrY", chr != "chrM")
clusters_table = as.data.table(clusters)
save(clusters_table, file = "~/isoviz/data/hESC_all_lfc_junctions.rda")

@@

Write function to generate intron coords from exon coords- this is currently slow (~30 minutes), can we make the loop more efficient?
This is only done for the gencode gtf for now which would be provided, this chunk would only need to run if people had their own gtf they wanted to use
```{r}
# make psl with intron coords instead of exon
# adapted from genomedata.R

@@

#to_plot = map_junction("ENSG00000001167.15") # NFYA
#to_plot = map_junction("ENSG00000100320") # RBFOX2, alt start is missing because it's intron doesnt overlap another and counts are only 8 so included in consitutive either

@@

Updated Function: Map junction to isoform: Updated to include all junctions and use gencode annotations to mark unique versus common
How do we incorporate expression here since the hESC data is more deeply sequenced- could combine feature counts when we format the leafcutter output
```{r}
# merge with gencode info and predictions from 230411_cas13_paper_figures.Rmd
# we should probably filter these for things like runs of T's, etc like we did when designing the screen
# missing 166- which are guides in Harm's screen
v41_info = read_tsv("~/isoviz/data/gencode_v41_all_junction_guides.txt", col_names = TRUE) %>% 
  mutate(guide_sequence = as.character(guide_sequence)) # 2,255,040
predictions = read_csv("/gpfs/commons/groups/knowles_lab/cas13_share/230414_predictions/combined-corrected-predictions-gencode.csv") %>% 
  select(guide_id, predicted_lfc) # 2,254,874

gencode_intron_all_data = v41_info %>% left_join(predictions, by = "guide_id")
save(gencode_intron_all_data, file = "~/isoviz/data/gencode_intron_all_data.rda")

# this gets read in within function: hESC_all_lfc_junctions.rda

# map junctions function
# I really don't need the guide info here just the junction info- consider revising and bring the guideRNAs in for another junction
map_all_junctions = function(gene = "ENSG00000100320", cell_type = "hESC"){

  # gencode- this is an updated file containing more junction info
  load(file = "~/isoviz/data/gencode_intron_all_data.rda")

  # filter for gene, for now, no need to filter for protein-coding since this gencode set only contains protein-coding
  # this now contains all guide information for this gene
  gene_iso_data = gencode_intron_all_data %>% filter(grepl(gene, gene_id))

  # join iso data with leafcutter data and mark any unannotated junctions
  # consider cell type
  lfc_clusters = paste0(cell_type, "_all_lfc_junctions")
  load(file = paste0("~/isoviz/data/", lfc_clusters, ".rda"))

  # test
  clusters_table %>% filter(chr == "chr22" & start > 35738735 & end < 36028824) %>% arrange(desc(start))

  # since leafcutter junctions dont have gene annotations, need to combine here first
  gene_cluster = gene_iso_data %>% 
    left_join(clusters_table, by = c("chr", "junc_start" = "start", "junc_end" = "end"))

  name = unique(gene_cluster$gene_name)
  gene_strand = unique(gene_cluster$strand)

  # to get information on leafcutter junctions that don't match annotation
  all_gene_clusters = clusters_table %>% filter(cluster.n %in% gene_cluster$cluster.n) %>% 
    left_join(gene_iso_data, by = c("chr", "start" = "junc_start", "end" = "junc_end")) %>%
    filter(is.na(gene_id)) %>% 
    mutate(gene_name = unique(gene_cluster$gene_name), strand = unique(gene_cluster$strand), 
           gene_id = unique(gene_cluster$gene_id), junction_category = "unknown", 
           transcript_isoforms = "unknown", junc_id = paste0("unk", 1:nrow(.))) %>%
    select(chr, junc_start = start, junc_end = end, everything()) %>%
    bind_rows(gene_cluster) %>%
    mutate(junc.counts = ifelse(is.na(cluster.n), 0, junc.counts), cluster.counts = ifelse(is.na(cluster.n), 0, cluster.counts))

  n = all_gene_clusters %>% distinct(cluster.n, junc_id) %>% group_by(cluster.n) %>% 
    mutate(junc.per.cluster = ifelse(is.na(cluster.n), 1, n())) %>% ungroup()

  all_gene_clusters %<>% left_join(n, by = c("cluster.n", "junc_id")) %>%
    mutate(junc.usage = ifelse(junc.counts == 0, 0, round((junc.counts/cluster.counts)*100, digits = 0)), cell_line = paste0(cell_type))

  #test
  all_gene_clusters %>% filter(grepl("209", transcript_isoforms)) %>%
    select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% arrange(junc_start)

  # create list of expressed isoforms
  # the logic is that if an isoform has a fully unique junction with no counts, it is unlikely to be expressed
  # I want to be careful here since some junctions won't be represented because of technical issues so only eliminate isoforms where none of their unique junctions have counts, avoid filtering on partially unique for now
  non_expressed_genes = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>% group_by(transcript_isoforms, junction_category) %>%
    mutate(isoform_counts = ifelse(junction_category == "fully_unique", sum(junc.counts), junc.counts)) %>% 
    filter(junction_category == "fully_unique" & isoform_counts == 0) %>% distinct(transcript_isoforms) %>% ungroup()

  uniquely_targetable = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>% filter(junction_category == "fully_unique") %>%
    distinct(transcript_isoforms)

  partially_targetable = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>% filter(junction_category == "partial_unique") %>%
    distinct(transcript_isoforms)

  output = all_gene_clusters %>% select(-guide_start, -guide_end, -guide_sequence, -target_sequence, -guide_id, -predicted_lfc) %>%
    distinct() %>% separate_longer_delim(transcript_isoforms, delim = ",") %>%
    mutate(transcript_targetable = ifelse(transcript_isoforms %in% uniquely_targetable$transcript_isoforms, "Uniquely", 
                                          ifelse(transcript_isoforms %in% partially_targetable$transcript_isoforms, "Partially", "None"))) %>% 
    mutate(isoform_expressed = ifelse(transcript_isoforms %in% non_expressed_genes$transcript_isoforms, "Unlikely", "Likely"))

  if(nrow(output) == 0){
    print(paste0("No junction reads detected for ", name, " in ", cell_type))
  }

test = map_all_junctions("ENSG00000100320", cell_type = "hESC")
test %>% filter(isoform_expressed == "Likely") %>% distinct(transcript_isoforms)

# chr22	35938897	36028240
```

```{r}
load(file='~/isoviz/data/iso_data_complete.rda')
#df = to_plot

@@

  # I am copying the plot_isoforms function here, figure out how to integrate these later
  gene = unique(df$gene_id)
  gene_trans = which(str_detect(iso_data_complete$gene_id, gene))
  gene_data = iso_data_complete[gene_trans,]

@@

#plot_junction_to_isoform(to_plot)
#ggsave("~/isoviz/plots/rbfox2_isoforms.pdf", width = 8, height = 8.5)
```

Updated plotting to go with all junctions output
```{r}
# might have to use regtools if I truly want all junctions
load(file='~/isoviz/data/iso_data_complete.rda')
df = test

# plot isoform plus leafcutter clusters
plot_all_junction_to_isoform = function(df, junction_usage = 5, include_common_juncs = FALSE, filter_expressed_isoforms = TRUE){

  # filter here based on input parameters
  if(include_common_juncs == FALSE){
    df %<>% filter(junction_category != "common")
  }

  if(filter_expressed_isoforms == TRUE){
    df %<>% filter(isoform_expressed == "Likely")
  }

  to_remove = df %>% filter(junc.per.cluster == 2 & (junc.usage < junction_usage | junc.usage > (100 - junction_usage)))
  df %<>% filter(!junc_id %in% to_remove$junc_id, junc.counts > 0)

  # get info after filtering
  name = unique(df$gene_name)
  transcripts = unique(df$transcript_isoforms)

  # filter transcripts for plotting too
  gene_data = iso_data_complete %>% filter(transcript_name %in% df$transcript_isoforms)

  # new code to plot leafcutter cluster info underneath isoform level data
  # aggregate isoform information
  text = df %>% separate(col = transcript_isoforms, into = c("name", "transcript")) %>% 
    mutate(transcript = ifelse(is.na(transcript), "unknown", transcript)) %>%
    group_by(cluster.n, junc_id) %>% 
    arrange(cluster.n, junc_id, transcript) %>%
    mutate(isoforms = paste0(transcript, collapse = ",")) %>%
    select(1:5, junc_id, junction_category, junc.usage, isoforms, junc.per.cluster) %>% distinct() %>% ungroup() %>% 
    mutate(text_plot = paste0(junc.counts, " reads (", junc.usage, "%) : ", isoforms))

  clusters = unique(df$cluster.n)
  introns = df %>% select(-gene_id, -gene_name, -transcript_isoforms) %>% 
    distinct() %>% arrange(cluster.n, junc_start)
  introns$junc.order = 1:nrow(introns)
  introns %<>% left_join(text)

  # for guides - remove this or print out?
  for_guides = introns %>% filter(grepl("junc", junc_id))

  p2 = ggplot() + 
    geom_rect(data = introns, mapping = aes(xmin = junc_start, xmax = junc_end, ymin = junc.order - 0.2, ymax = junc.order + 0.2, fill = cluster.n)) + 
    geom_text(data = introns, aes(x = junc_end, y = junc.order, label = text_plot), hjust = 0, size = 3) +
    xlim(min_start, max_end) + theme_bw() + 
    xlab("Hg38 Genomic Position (bp)") + ylab("") + 
    geom_text(data = introns, aes(x = Inf, y = junc.order, hjust = 0, label = junc_id), size = 3) + 
    theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "none", plot.margin = margin(0,1,0,0.1, "in")) +
    coord_cartesian(xlim = c(min_start, max_end), clip = 'off')

  # plot dimenstions based on number of isoforms and junctions
  t = (n + nrow(introns))
  h = t/2
  p1_p2 = plot_grid(p1, p2, ncol = 1, align = "v", rel_heights = c(n*0.8, nrow(introns)))

  return(p1_p2)
}

ggsave("~/isoviz/plots/rbfox2_test.pdf", width = 8, height = h)

#df %>% filter(transcript_isoforms == "RBFOX2-209") %>% arrange(junc_start)
```

Function to get guide RNA predictions for specific junctions
```{r}
# need to read in count information a different way- this is just a quick and dirty method
# write a function to get expressed junctions/isoforms and call that within functions?
get_guide_predictions = function(gene = "ENSG00000100320", cell_type = "hESC", guides_per_junction = 2){
  load(file = "~/isoviz/data/gencode_intron_all_data.rda")
  gene_guides = gencode_intron_all_data %>% filter(grepl(gene, gene_id))
  gene_name = unique(gene_guides$gene_name)
  top_guides = gene_guides %>% filter(junction_category == "partial_unique" | junction_category == "fully_unique") %>%
    group_by(junc_id) %>% slice_min(predicted_lfc, n = guides_per_junction)

  # filter junctions based on expression or by junc_id- this is just set up to get an example

  output = top_guides %>% filter(junc_id %in% for_guides$junc_id) %>% 
    left_join(for_guides) %>%
    select(Cluster = cluster.n, JuncID = junc_id, Category = junction_category, Counts = junc.counts, Usage = junc.usage,
           Isoforms = isoforms, GuideID = guide_id, GuideSeq = guide_sequence, Prediction = predicted_lfc)

  # output table
  # don't add sig digits
  fun <- function(x) {formatC(x, format = "f", digits = 0)}

  return(nice_table(output, col.format.custom = 4:5, format.custom = "fun", 
                    title = paste0(gene_name, ": Top ", guides_per_junction, " gRNAs per Junction")))
}

guide_table = get_guide_predictions("ENSG00000100320")

flextable::save_as_docx(guide_table, path = "~/isoviz/plots/230420_rbfox2_guides_table.docx")
```

@@

to_plot = map_junction("ENSG00000001167.15", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/nfya_isoforms_hESC.pdf", width = 8, height = 5)

@@

to_plot = map_junction("ENSG00000100320", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/rbfox2_isoforms_hESC.pdf", width = 8, height = 8.5)

# PTBP1
to_plot = map_junction("ENSG00000011304", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/ptbp1_isoforms_hESC.pdf", width = 8, height = 8.5)

to_plot = map_junction("ENSG00000011304", cell_type = "HEK293") 
plot_junction_to_isoform(to_plot) # no unique junctions here, fix code

to_plot = map_junction("ENSG00000011304", cell_type = "A375") 
plot_junction_to_isoform(to_plot) # no unique junctions here

# MKNK2
to_plot = map_junction("ENSG00000099875", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/mknk2_isoforms_hESC.pdf", width = 8, height = 4)

to_plot = map_junction("ENSG00000099875", cell_type = "HEK293") 
plot_junction_to_isoform(to_plot)

to_plot = map_junction("ENSG00000099875", cell_type = "A375") 
plot_junction_to_isoform(to_plot)

# HNRNPA1
to_plot = map_junction("ENSG00000135486", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/hnrnpa1_isoforms_hESC.pdf", width = 8, height = 5.5)

# HNRNPK
to_plot = map_junction("ENSG00000165119", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/hnrnpk_isoforms_hESC.pdf", width = 16, height = 6)

# KHSRP- ENSG00000088247
to_plot = map_junction("ENSG00000088247", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/khsrp_isoforms_hESC.pdf", width = 16, height = 6)

# MATR3
to_plot = map_junction("ENSG00000015479", cell_type = "hESC_med_string") 
plot_junction_to_isoform(to_plot)
ggsave("~/isoviz/plots/matr3_isoforms_hESC.pdf", width = 16, height = 6)

@@
